A Critical Appraisal of Zero-Multiple Method in Simulation Biomolecular Systems

### 2014-10-29 writedown/zm/report/report.tex

\begin{table}
  \centering
  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$ and viscosity $\eta$
    calculated by different methods.    
    The parenthesises in the last column show the statistical uncertainty
    at the confidence level of 95~\%.
    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
  }
  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}ccc ccccc}\hline\hline
    Method      &   $r_c$ &    $l$      & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$ \\
                &    [nm] &             &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
    % Method      &   $r_c$ [nm] &    $l$      & $\mu^\exc$ [kJ/mol] &$C_{v,m}$ [J/(mol K)] & $\eps$ (Sys.~$\systemsb$) & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] &  $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
    SPME        &         1.9     &       --      &      $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
    RF          &         1.2     & --            &      $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\
    ZM          &         1.2     &       1       &      $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
    ZM          &         1.2     &       2       &      $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
    ZM          &         1.2     &       3       &      $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
    ZM          &         1.2     &       4       &      $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp3}
\end{table}
    % SPME        &         1.9     &       --      & 1.67049 (0.00014)     $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
    % RF          &         1.2     & --            & 1.66733 (0.00016)      $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\
    % ZM          &         1.2     &       1       & 1.67052 (0.00022)     $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
    % ZM          &         1.2     &       2       & 1.67029 (0.00013)     $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
    % ZM          &         1.2     &       3       & 1.67024 (0.00018)     $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
    % ZM          &         1.2     &       4       & 1.67031 (0.00010)     $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\

\begin{table}
  \centering
  \caption{The constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
    thermal expansion coefficient $\alpha$
    calculated by different methods.    
    The parenthesises in the last column show the statistical uncertainty
    at the confidence level of 95~\%.
    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
  }
  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}ccc ccc}\hline\hline
    Method      &   $r_c$ [nm] &    $l$      & $\kappa_T$ [$10^{-10}\textrm{m}^2/\textrm{N}$] & $C_{p,m}$ [J/(mol K)] & $\alpha$ [$10^{-3}\textrm{K}^{-1}$]\\\hline
    SPME        &         1.9     &       --      & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
    RF          &         1.2     & --            & \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\
    ZM          &         1.2     &       1       & 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
    ZM          &         1.2     &       2       & 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
    ZM          &         1.2     &       3       & 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
    ZM          &         1.2     &       4       & 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp3a}
\end{table}

@@

>>>>

\begin{table}
  \centering
  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$ and viscosity $\eta$
    calculated by different methods.    
    The parenthesises in the last column show the statistical uncertainty
    at the confidence level of 95~\%.
    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
  }
  \begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}cccc ccccc}\hline\hline
    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$ \\
                &    [nm] &        & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
    % Method      &   $r_c$ [nm] &    $l$      & $\mu^\exc$ [kJ/mol] &$C_{v,m}$ [J/(mol K)] & $\eps$ (Sys.~$\systemsb$) & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] &  $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
    SPME        &1.9 & -- &    & $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
    RF          &1.2 & -- &--  & $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\\hline
    ZM          &1.2 & 1  &0.0 & $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
    ZM          &1.2 & 1  &0.5 & $-26.36$ (0.30) & 72.25 (0.78)  & 97.1 (2.2)  & \textbf{5.52} (0.25)   & \textbf{0.339} (0.008)\\ 
    ZM          &1.2 & 1  &1.0 & $-26.01$ (0.22) & 72.44 (0.84)  & 96.2 (2.3)  &        {5.78} (0.25)   & \textbf{0.330} (0.011)\\ 
    ZM          &1.2 & 1  &1.5 & $-26.03$ (0.24) & 71.31 (0.78)  & 99.1 (2.5)  & \textbf{5.71} (0.09)   &        {0.312} (0.008)\\ 
    ZM          &1.2 & 1  &2.0 & $-26.14$ (0.34) & 71.27 (0.78)  & 95.9 (2.5)  &        {5.90} (0.04)   &        {0.307} (0.007)\\ \hline
    ZM          &1.2 & 2  &0.0 & $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
    ZM          &1.2 & 3  &0.0 & $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
    ZM          &1.2 & 4  &0.0 & $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp3}
\end{table}
    % SPME        &         1.9     &       --      & 1.67049 (0.00014)     $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
    % RF          &         1.2     & --            & 1.66733 (0.00016)      $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\
    % ZM          &         1.2     &       1       & 1.67052 (0.00022)     $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
    % ZM          &         1.2     &       2       & 1.67029 (0.00013)     $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
    % ZM          &         1.2     &       3       & 1.67024 (0.00018)     $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
    % ZM          &         1.2     &       4       & 1.67031 (0.00010)     $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\

\begin{table}
  \centering
  \caption{The constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
    thermal expansion coefficient $\alpha$
    calculated by different methods.    
    The parenthesises in the last column show the statistical uncertainty
    at the confidence level of 95~\%.
    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
  }
  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cccc ccc}\hline\hline
    Method      &   $r_c$ [nm] &    $l$ & $\alpha$ [$\textrm{nm}^{-1}$]     & $\kappa_T$ [$10^{-10}\textrm{m}^2/\textrm{N}$] & $C_{p,m}$ [J/(mol K)] & $\alpha$ [$10^{-3}\textrm{K}^{-1}$]\\\hline
    SPME        &  1.9     &       -- &    & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
    RF          &  1.2     & --       &    & \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\\hline
    ZM          &  1.2     &       1  & 0.0& 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
    ZM          &  1.2     &       1  & 0.5& 5.920 (0.050)               &78.90 (0.92)           &\textbf{1.003} (0.016) \\
    ZM          &  1.2     &       1  & 1.0& 5.946 (0.050)               &78.37 (0.92)           &1.008 (0.016)          \\
    ZM          &  1.2     &       1  & 1.5& 5.974 (0.050)               &80.23 (0.86)           &1.040 (0.017)          \\
    ZM          &  1.2     &       1  & 2.0& \textbf{6.052} (0.051)      &79.41 (0.91)           &1.045 (0.016)          \\\hline
    ZM          &  1.2     &       2  & 0.0& 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
    ZM          &  1.2     &       3  & 0.0& 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
    ZM          &  1.2     &       4  & 0.0& 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp3a}
\end{table}

@@

\subsection{Damping effect}

In this section we investigate the damping effect. The pressure is plotted as a function of  the cut-off radius is plotted for different choices of
the splitting parameter $\alpha$ in Fig.~\ref{fig:damp-pres}. The system for the simulation was $L_0$.
\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l1.eps}
  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}\\
  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l3.eps}
  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
  \caption{The pressure convergence with respect to the cut-off radius.
    For ZM method, different splitting parameter $\alpha$ (in unit of $\textrm{nm}^{-1}$) are shown for different orders:  $l=1$, 2, 4, and 4.
  }
  \label{fig:damp-pres}
\end{figure}

The convergence of the integrated auto-correlation function $I_\eta(T) $ is shown in Fig.~\ref{fig:damp-vis-l1}.
\begin{figure}
  \centering
  \includegraphics[]{fig/result.tiny/fig-vis-l1-damp.eps}
  \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $. The error bars indicating 95\% confidence level are plotted with the SPME method. The different splitting parameters for ZM $l=1$ method are plotted}
  \label{fig:damp-vis-l1}
\end{figure}

The RDF is plotted for different splitting parameters $\alpha$ for ZM $l=2$ and 3 in Fig.~\ref{fig:damp-rdf-l23}. Higher $\alpha$ reproduces the RDF better.
The system was $L_1$.
\begin{figure}[]
  \centering
  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l2-damp.eps}
  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l3-damp.eps}
  \caption{Radial distribution function for different splitting parameters $\alpha$ for ZM $l=2$ (left) and $l=3$ (right).}
  \label{fig:damp-rdf-l23}
\end{figure}

The Kirkwood G-factor is plotted for different splitting parameters $\alpha$ for ZM $l=2$ and 3 in Fig.~\ref{fig:damp-gkr-l23}. 
The system was $L_1$.
\begin{figure}[]
  \centering
  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-gkr-l2-damp.eps}
  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-gkr-l3-damp.eps}
  \caption{Kirkwood G-factor for different splitting parameters $\alpha$ for ZM $l=2$ (left) and 3 (right).}
  \label{fig:damp-gkr-l23}
\end{figure}
